### 2021-03-15 paper.Rmd
add panel for neural network examples

> figure 16 panel a and b

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=0.5\textwidth]{figures/scheidigger_nn_tour.png}
          \includegraphics[width=0.5\textwidth]{figures/scheidigger_umap_tour.png}
\caption{Left: A grand tour run on the output of a deep neural network model for classification. Right: A grand tour on UMAP components of a layer of deep neural network.}
\label{fig:tour-nn}
\end{figure*}
